The Three Corridors

### 2015-01-24 msr.tex
added bibliographic entries
working on introduction

Software metrics provide a means to extract useful and measurable information about the structure of a software system. Since software artefacts consist of digital data, many of their aspects are easily measured. This explains why the first metrics like LOC (Lines Of Code) and CLOC (Comment Lines of Code) appeared very early. Over the years, a wealth of different metrics has appeared in the literature \cite{GUSC07,BBM96,LOKI94,HK81,BDM97} and some of them, like Chidamber and Kemerer \cite{CHKE94} have found their way in software development practice and tools.

Today a software engineer or developer has a very large list of metrics at his disposition in order to gain the required insight for understanding and evaluating the size, complexity and overall structure of a system. This has led researchers to try to discover which set of metrics is most appropriate for each environment \cite{XSZC00,PUVA03,MAHA99,BRCA94}. There also exist metrics that can be used to evaluate other aspects of a system, such as the process that was used to develop it.

>>>>

Software metrics provide a means to extract useful and measurable information about the structure of a software system. Since software artefacts consist of digital data, many of their aspects are easily measured. This explains why the first metrics like LOC (Lines Of Code) and CLOC (Comment Lines of Code) appeared very early. Over the years, a wealth of different metrics has appeared in the literature and some of them, like Chidamber and Kemerer \cite{CHKE94} and those presented by Lorenz et al. \cite{LOKI94} that have found their way in software development practice and tools. Today a software engineer or developer has a very large list of metrics at her disposition in order to gain the required insight for understanding and evaluating the size, complexity and overall structure of a system.
